Towards understanding the central limit theorem by learning Python basics

### 2021-04-06 paper/article.tex
Add link to online materials
Update text after Andreas Lindner's suggestions

Connecting pure mathematics and real life or virtual experiments, can be, to our experience,
extremely hard. Probability is an important item of the curriculum at secondary level,
thus it is also an important item in the teacher training. But, to our experience,
most prospective teachers \textit{never} understand the basics beyond introductory level.
Our conjecture is that the main problem lies in students' verification if theory indeed meets practice,
so, at the end of the day, a very uncertain knowledge can be observed in the students' perception. As a consequence,
in most cases, not just yesterday's and today's mathematics teachers cannot connect
theory and practice, but their students either. Roughly speaking: everybody talks about probability and
statistics, but nearly nobody understands anything behind the scenes.

@@

On the other hand, in the field of data science
Python is currently the mostly used programming language. Especially in
machine learning, which could be seen as an advanced application of
probability, Python is very popular. We think that students who believe
that the exercises they solve are not artificially constructed for the
course, but have some connection to the real world, will be more
motivated. As a teacher we can give students the impression that if they
use Python in their introductory course on probability, they take a first
step into the prestigious field of data science. This may increase the
motivation of students and as a result they will achieve higher.

@@

Importantly, we simplified and minimized the code we used during the email course.
This pre-process required several discussions among the authors to avoid
the technical difficulties of the programming language, but still allow
obtaining simple outputs. We had to balance between readability, simplicity,
elegance and speed. We learned that Python itself could be improved to
have simpler constructions than the \texttt{for i in range(...)} loop for iteration.
At the end of day we were still satisfied with all of the code and the students'
solutions confirm that our choices were acceptable.

@@

@@

We are thankful to the students Alexander, Romana, Sandra and Sarah
for their participation in the project.

>>>>

Connecting pure mathematics and real life or virtual experiments, can be, to our experience,
extremely hard. Probability is an important item of the curriculum at secondary level,
thus it is also an important item in the teacher training. But, to our experience,
many prospective teachers have difficulties \textit{even with the basics} beyond introductory level.
Our conjecture is that the main problem lies in students' verification if theory indeed meets practice,
so, at the end of the day, a very uncertain knowledge can be observed in the students' perception. As a consequence,
in most cases, not just yesterday's and today's mathematics teachers cannot connect
theory and practice, but their students either. Roughly speaking: everybody talks about probability and
statistics, but just a few have \textit{real understanding} behind the scenes.

@@

On the other hand, in the field of data science
Python is currently the mostly used programming language. Especially in
machine learning, which could be seen as an advanced application of
probability, Python is very popular. We think that students who believe
that the exercises they solve are not artificially constructed for the
course, but have some connection to the real world, will be more
motivated. As a teacher we can give students the impression that if they
use Python in their introductory course on probability, they take a first
step into the prestigious field of data science. This may increase the
motivation of students and as a result they will achieve a higher level.

@@

Importantly, we simplified and minimized the code we used during the email course.
This pre-process required several discussions among the authors to avoid
the technical difficulties of the programming language, but still allow
obtaining simple outputs. We had to balance between readability, simplicity,
elegance and speed. We learned that Python itself could be improved to
provide a simpler way to construct iterations than the usual \texttt{for i in range(...)} loop.
At the end of the day we were still satisfied with all of the code and the students'
solutions confirm that our choices were acceptable.

@@

All materials of our project---including the Python programs, the homework assignments and
the turned-in homework---can be found online at \url{https://github.com/kovzol/probability-python}.

@@

We are thankful to the students Alexander, Romana, Sandra and Sarah
for their participation in the project, and to Andreas Lindner who
gave us useful feedback on the first version of the manuscript.
